### 2018-10-10 paper/finitecomplete-failures.tex
Added complete testing assumption and re-phrased Case 2 of Lemma 8.

@@

\medskip
\noindent {\bf Case~2.} We note that trace $s$ is again a trace of the
product graph $G$, but we do not know its length. Again, by applying
Lemma~\ref{lemma:reachproduc}, we know that the state $G/s$ can be reached by
a trace $u\in\trc(Q)\cap\trc(P)$ of maximal length $\#u < pq$. We consider
the test $U_F(\# u)$, for which $U_F(\# u)/u = U_F(\#u,\#u,G(P)/u)$, because
of Lemma~\ref{lemma:ufproperties}. Test $U_F(\#u)$  always performs branch
(\ref{eq:ufc}) until the trace $u$ has been completely processed. \fixme{If
the SUT accepts it? See previous fixme.} $U_F(\#u,\#u,G(P)/u)$ may execute
branches (\ref{eq:ufa}) or (\ref{eq:ufd}) only:~assumption
(\ref{eq:accsnotcontained}) in Case~2 implies that $P/s$ has at least one
non-empty minimal acceptance. From (\ref{eq:minhitminaccempty}) we know that
this is equivalent to $\minhits(P/s) = \minhits(G(P)/s)\neq\varnothing$, and
we observe that $G(P)/s = G(P)/u$, so $\minhits(G(P)/u)\neq\varnothing$. As a
consequence, branch (\ref{eq:ufb}) cannot be taken because its guard
condition evaluates to $\isf$  for $U_F(\#u,\#u,G(P)/u)$. The guard condition
$(k < j)$ for branch (\ref{eq:ufc}) evaluates to $\isf$ for
$U_F(\#u,\#u,G(P)/u)$, too. If branch (\ref{eq:ufa}) is executed, the test
always fails. If branch (\ref{eq:ufd}) is executed, the test fails for the
execution where a minimal hitting set $H\in\minhits(P/u)$ is chosen by
$U_F(\#u,\#u,G(P)/u)$ that has an empty intersection with the minimal
acceptance $A_Q$ from condition (\ref{eq:accsnotcontained}). The existence of
such an $H$ is guaranteed because of Lemma~\ref{lemma:hseta}. As a
consequence, there exists a test execution   where $Q/u$ selects acceptance
$A_Q$ and $U_F(\#u,\#u,G(P)/u)$ selects $H$. This execution deadlocks in
process state $(Q\parallel[\Sigma]U_F(\# u))/u$, so it cannot produce the
$\epass$-event; this means that the test fails. This concludes the proof.
\xbox
\end{proof}
%
Our notion of tests can be specialised to deal with traces refinement, as we
explain in Section~\ref{sec:finitecomplete}.
The next section presents and example.

>>>>

% -------------------------------------------------------------------------
\subsubsection*{Complete Testing Assumption}
As explained above, passing a test case $U_F(j)$ requires that none of 
the possible executions $(Q\parallel[\Sigma] U_F(j))$ stops after $\efail$ or
stops without having produced event $\epass$. Therefore, it is necessary to determine
whether all possible executions have been covered in the repeated runs of 
$(Q\parallel[\Sigma] U_F(j))$.  
The theoretical completeness results are therefore based on
a  \emph{complete testing
assumption}~\cite{hierons_testing_2004,DBLP:conf/icfem/CavalcantiG07}, 
 which means that every
possible behaviour of the SUT is performed after a finite number of test
executions. In practice, this is realised by executing each test several
times, recording the traces that have been performed, and using hardware or
software coverage analysers to determine whether all possible test execution
behaviours of the SUT have been observed. Therefore, 
testing nondeterministic SUTs 
  comes
at the price of having to apply some grey-box testing techniques enabling us
to decide whether all SUT behaviours have been observed.

@@

\medskip
\noindent {\bf Case~2.} We note that trace $s$ is again a trace of the
product graph $G$, but we do not know its length. Again, by applying
Lemma~\ref{lemma:reachproduc}, we know that the state $G/s$ can be reached by
a trace $u\in\trc(Q)\cap\trc(P)$ of maximal length $\#u < pq$. We consider
the test $U_F(\# u)$, for which $U_F(\# u)/u = U_F(\#u,\#u,G(P)/u)$, because
of Lemma~\ref{lemma:ufproperties}. Test $U_F(\#u)$  always performs branch
(\ref{eq:ufc}) until the trace $u$ has been completely processed.  
 $U_F(\#u,\#u,G(P)/u)$ may execute
branches (\ref{eq:ufa}) or (\ref{eq:ufd}) only:~assumption
(\ref{eq:accsnotcontained}) in Case~2 implies that $P/s$ has at least one
non-empty minimal acceptance. From (\ref{eq:minhitminaccempty}) we know that
this is equivalent to $\minhits(P/s) = \minhits(G(P)/s)\neq\varnothing$, and
we observe that $G(P)/s = G(P)/u$, so $\minhits(G(P)/u)\neq\varnothing$. As a
consequence, branch (\ref{eq:ufb}) cannot be taken because its guard
condition evaluates to $\isf$  for $U_F(\#u,\#u,G(P)/u)$. The guard condition
$(k < j)$ for branch (\ref{eq:ufc}) evaluates to $\isf$ for
$U_F(\#u,\#u,G(P)/u)$, too. If branch (\ref{eq:ufa}) is executed, the test
always fails. If branch (\ref{eq:ufd}) is executed, the test   deadlocks and therefore 
fails for the
execution where 
$Q/u$ selects the minimal acceptance $A_Q$ as specified in (\ref{eq:accsnotcontained})
and $U_F(\#u,\#u,G(P)/u)$ selects 
a minimal hitting set $H\in\minhits(P/u)$ which has an empty intersection with   $A_Q$.
The existence of
such an $H$ is guaranteed because of Lemma~\ref{lemma:hseta}. As a
consequence,   $(Q\parallel[\Sigma]U_F(\# u))/u$,   cannot produce the
$\epass$-event in this execution; 
this means that the test fails. The complete testing assumption guarantees that 
this execution really occurs if $(Q\parallel[\Sigma]U_F(\# u))$ is executed sufficiently often.
This concludes the proof.
\xbox 
\end{proof}
%
Our notion of tests can be specialised to deal with traces refinement, as we
explain in Section~\ref{sec:finitecomplete}.
The next section presents and example.
